---
title: Download all the data
execute:
  echo: false
params:
  data_version: "default_version"
---

```{r}
#| include: false
#| message: false
library(tidyverse)
library(targets)
library(kableExtra)
library(janitor)

all_data = tar_read(all_data)

data_version = all_data |> 
  filter(row_number() == 1) |> 
  pull(data_version)

```

This site provides all of the data underlying the [EPI State of Working America Data Library](https://data.epi.org). If you only need a small subset of data, it might be easiest to just use the [EPI Data Library](https://data.epi.org). 

But if you want *all* of the data:

## Downloads

Download .csv files of latest version of the data, Version `r data_version`: [epi_swa_data_library.zip](https://github.com/Economic/data/releases/latest/download/epi_swa_data_library.zip)

Archived versions of the data are [here](https://github.com/Economic/data/releases/).

## Citation

If you use the data, please cite it:

::: {.callout-note}
## Source
Economic Policy Institute. 2024. State of Working America Data Library, Version `r data_version`. <https://data.epi.org>.
:::

## Data file contents

[epi_swa_data_library.zip](https://github.com/Economic/data/releases/latest/download/epi_swa_data_library.zip) is a zipped collection of .csv files, where each file is a particular "indicator" or outcome on the EPI State of Working America Data Library.

The current release of the data contains the following .csv files:

```{r}
all_data |>
  distinct(indicator) |>
  mutate(
    file_name = make_clean_names(indicator),
    file_name = paste0(file_name, ".csv")
  ) |>
  select(file_name, indicator) |>
  arrange(file_name) |>
  kable(col.names = c("File name", "Indicator"))
```

## File contents

Each .csv file contains the following columns

```{r}
all_data |>
  colnames() |>
  as_tibble() |>
  rename(col_name = value) |>
  mutate(col_description = case_match(
    col_name,
    "data_version" ~ "Version of the data",
    "indicator" ~ "Indicator",
    "measure" ~ "Outcome measure",
    "date_interval" ~ "Time frequency of the data: 'year', 'quarter', or 'month'",
    "year" ~ "Year",
    "quarter" ~ "Quarter",
    "month" ~ "Month",
    "geo_type" ~ "Geography type: 'national', 'state', 'division', or 'region'",
    "geo_name" ~ "Geography name",
    "geo_code" ~ "Numeric geographic identifier",
    "group" ~ "Group: e.g, 'Gender' or 'Race/Ethnicity X Gender'",
    "group_value" ~ "Group value: e.g., 'Female' or 'Hispanic X Female'",
    "value" ~ "Data value"
  )) |>
  kable(col.names = c("Column name", "Column description"))
```

Each time series in the EPI Data Library is a unique combination of the columns `indicator` `geo_name` `measure` `year` `month` `quarter` `group_value`

Each row of the data represents a value from a given time series.

